Deep learning for geophysics

### 2024-06-02 manuscript.tex
Fix page numbering
And tweak acknowledgements

Tasman, for being a good friend and inspirational colleague for most of my academic career --- looking forward to sharing a project again sometime, somewhere in the future!
Lu, for sharing your incredible amount of geophysics knowledge, incredible cooking, and love of tennis with me.
Matilda, for being a wonderful friend and the best housemate --- Thanks for being silly with me.

My first floor colleagues and fellow tech geeks, David, Daniel, Chris, Minh, and Peter --- Your friendship and knowledge has been a wonderful environment to grow in as a geodata scientist.
And all my SES, CET, and friends beyond: Alex, Anne, Ben, France, Jackson, Jess, Jules, Kailah, Lauren, Lauri, Liam, Lilly, Maddie, Maria, Malvina, Nicolas, Ravi, Sean, Sumail, Vickie, and Ze --- Thank you for years of lunches, dinners, beaches, rock climbing, yoga, and all the opportunities to talk rocks that I've been missing.

@@

\pagenumbering{arabic}
\setcounter{page}{1}
\setcounter{section}{0}
% \renewcommand{\thesection}{\arabic{section}}

@@

\pagestyle{body}
\chapter{Introduction}
\label{ch:intro}
% \newrefsection{}
\input{intro}

>>>>

Tasman, for being a good friend and inspirational colleague for most of my academic career --- looking forward to sharing a project again sometime, somewhere in the future!
Lu, for sharing your incredible amount of geophysics knowledge, incredible cooking, and love of tennis with me.
Matilda, for being a wonderful friend and the best housemate --- thanks for being silly with me.

My first floor colleagues and fellow tech geeks, David, Daniel, Chris, Minh, and Peter --- Your friendship and knowledge has been a wonderful environment to grow in as a geodata scientist.
And all my SES, CET, and friends beyond: Alex, Anne, Ben, France, Jackson, Jess, Jules, Kailah, Lauren, Lauri, Liam, Lilly, Maddie, Malvina, Maria, Nicolas, Ravi, Sean, Sumail, Vickie, and Ze --- Thank you for years of lunches, dinners, beaches, rock climbing, yoga, and all the opportunities to talk rocks that I've been missing.

@@

% \renewcommand{\thesection}{\arabic{section}}

@@

\pagestyle{body}

\chapter{Introduction}
\label{ch:intro}

\pagenumbering{arabic}
\setcounter{page}{1}
\setcounter{section}{0}
% \newrefsection{}
\input{intro}
